Hypertension and microbiome

### 2019-01-02 rrbiome.Rmd
Lactobacillus

```{r Reading maaslins output}
maas.results.df.signf <- read.table("maaslin/merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
           Beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

@@

```{r lactobacillus, eval = FALSE}
pseq.lacto  <- subset_taxa(pseq.species, Genus=="Lactobacillus")
pseq.lacto.comp  <- microbiome::transform(pseq.lacto, "compositional")
abud.rel.lacto <- abundances(pseq.lacto.comp)

abud.rel.lacto %>%
    gather(Key, Value) %>%
    group_by(Subject, Type) %>%
     summarise_each(funs(mean= mean(., na.rm=TRUE)))

```

>>>>

```{r Reading maaslins output}
maas.results.df.signf <- read.table("maaslin/maaslin_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
           Beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

@@

```{r lactobacillus}
pseq.lacto  <- subset_taxa(pseq.species, Genus=="Lactobacillus")
pseq.lacto.comp  <- microbiome::transform(pseq.lacto, "compositional")
abud.rel.lacto <- abundances(pseq.lacto.comp)

abud.rel.lacto %>%
    t %>%
    as.data.frame %>%
    #dplyr::select("Lactobacillus_paracasei (BacteriaPlasmid)", "Lactobacillus_selangorensis (Bacteria)") %>%
    gather(key, value) %>%
    group_by(key) %>%
    summarise_all(funs(mean= mean(value),
                       min = min(value),
                       max = max(value),
                       sd = sd(value),
                       n = n(),
                       nonzeros = sum(abs(value) > 1e-12),
                       zeros = n - nonzeros)) %>%
    arrange(zeros) %>%
    kable
```
